A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-28 tex-arxiv/article.tex
add a paragraph about qualitative results in discussion

Comparing the two proposed model architectures by their best attained values, in terms of distribution similarity measures such as cosine similarity and Euclidean distance, the results are generally quite good for both, with the RNN having the edge in most distance measures but notably one of the feedforward models demonstrating the highest cosine similarity. In terms of step-wise metrics, RNN models are typically better show better results -- which is perhaps to be expected, given that their inputs contain all previous states in the trajectory rather than a single observation.

>>>>

The qualitative aspects of our results -- the visual representations of trajectories and their characteristics when executed on a real robot -- closely resemble throwing motions as executed by the human experts, suggesting that the selected approach to data collection is adequate for encoding the key features of this task. The same can be said for the fact that a large minority of the feedforward models and a majority of the recurrent ones were able to reproduce a complete throw trajectory for every set of initial conditions in the training and validation data sets. The most important takeaway regarding this aspect of our approach is that augmenting the data with time step information is important to achieve good performance.

Comparing the two proposed model architectures by their best attained values, in terms of distribution similarity measures such as cosine similarity and Euclidean distance, the results are generally quite good for both, with the RNN having the edge in most distance measures but notably one of the feedforward models demonstrating the highest cosine similarity. In terms of step-wise metrics, RNN models typically show better results -- which is perhaps to be expected, given that their inputs contain all previous states in the trajectory rather than a single observation.
